Analysis for Project

### 2021-11-23 analysis/analysis.Rmd
Add asis results for monoracial outcome table

```{r monoracial-results, warning=FALSE}
results_monoracial <- map(list(model0, model1, model2, model3, model4),
                          function(x) {
                            marg(x, "race", type="effects", 
                                 vcov_mat=vcovCL(x, cluster=acs$cluster),
                                 at_var_interest=c("White","Black","Indigenous",
                                                   "Asian","Latino"))[[1]][-1,]
                          })

>>>>

```{r monoracial-results, warning=FALSE, results='asis'}
results_monoracial <- map(list(model0, model1, model2, model3, model4),
                          function(x) {
                            marg(x, "race", type="effects", 
                                 vcov_mat=vcovCL(x, cluster=acs$cluster),
                                 at_var_interest=c("White","Black","Indigenous",
                                                   "Asian","Latino"))[[1]][-1,]
                          })
